---
title: "Models"
author: "SriRitvik Yellamilli"
format: html
---
```{r}
#| label: setup
#| message: FALSE
library(gtsummary)
library(tidyverse)
library(brms)
library(tidybayes)
```
```{r}
#| label: plot
fit_bern |> 
  add_epred_draws(newdata = ndata) |> 
  select(.epred) |> ggplot(aes(x = .epred, y = after_stat(count / sum(count)))) + geom_density() + 
  scale_x_continuous(labels = scales::percent_format()) + scale_y_continuous(labels = scales::percent_format()) + labs(title = "Posterior Distribution for p", subtitle = "There is a 95% chance for a value between 40% and 45%.", x = "Proportion, p, of Votes for Biden", y = "Probability")
```
In this project, we aimed to predict the proportion of votes that will be cast for Joe Biden in the 2024 election. By using an intercept-only Bernoulli model, we estimated the expected value of this proportion. Our analysis indicates that there is a 95% chance that the proportion of votes for Biden will be between 40% and 45%. This estimate is based on the data we collected and the model we built, providing a measure of uncertainty around the predicted value.

$$ biden_i =  \mu + \epsilon_i $$
```{r}
#| label: model
#| cache: true
fit_bern <- brm(formula = biden ~ 1,
    data = poll_data,
    family = bernoulli(),
    refresh = 0,
    silent = 2,
    seed = 9)
```
